Bayesian Restricted Likelihood Methods: Conditioning on Insufficient Statistics in Bayesian Regression\thanksref{T1}

### 2020-11-02 revision_2/response/Drafts of response to referees/responseV4.tex
clean up and add abc analysis script

We have taken the following steps to address your comment.  We now

\begin{enumerate}
\item Point out that M-estimators have been our default choice in the very first illustrative example:
 \response{Details of these estimators can be found in many places, including \citep{huber2009}. We return to the two M-estimators throughout this paper as we have found them to offer good default choices for practitioners dealing with outliers. A short review of these estimators is provided in the Supplementary Material.}
 \item Include a short review of M-estimators in the Supplement
 \item Include `Practical Considerations for Using the Restricted Likelihood' to the Supplement. 
\end{enumerate}
}

@@

\response{At the end of Section 3 (note renumbering of sections) we have included a paragraph:}

\response{'Finally, it is clear the estimators themselves must be computed for every iteration of the Markov Chain. We have found this burden to be marginal in comparison to computing the needed Jacobian. In the simulations and real data analyses presented below, we will see that the additional computational expense needed to fit the Bayesian model is often worthwhile, leading to better performance compared to traditional, non-Bayesian robust regression estimators.  This is most evident when substantive prior information is available and information in the data is limited.'}

\response{Additionally, we have included a paragraph in the introduction discussing advantages and disadvantages of the new method.}
%}

>>>>

We have taken the following steps to address your comment:

\begin{enumerate}
\item Point out that M-Estimators have been our default choice in the very first illustrative example:
 \response{Details of these estimators can be found in many places, including \citep{huber2009}. We return to the two M-estimators throughout this paper as we have found them to offer good default choices for practitioners dealing with outliers. A short review of these estimators is provided in the Supplementary Material.}
 \item Included a short review of M-Estimators in the Supplement
 \item Included `Practical Considerations for Using the Restricted Likelihood' to the Supplement. 
\end{enumerate}
}

@@

\response{At the end of section 4 we have included a paragraph:}

\response{'Finally, it is clear the estimators themselves must be computed for every iteration of the Markov Chain. We have found this burden to be marginal relative to computation of the needed Jacobian. In the simulations and real data analyses presented below, we will see that the additional computational expense needed to fit the Bayesian model is often worthwhile, leading to better performance compared to traditional, non-Bayesian robust regression estimators.  This is most evident when substantive prior information is available and information in the data is limited.'}

\response{Additionally, we have included a paragraph in the introduction discussing advantages and disadvantages of the new method.}
}

### 2020-11-02 revision_2/response/Drafts of response to referees/responseV6.tex
clean up and add abc analysis script

\response{This idea is in perfect alignment with our work.  You are right that $T(yobs)$ need not be unbiased -- in fact, it need not even be an estimator (think of sums of squares in an ANOVA setting as opposed to mean squares).  It is merely a statistic upon which we condition when using Bayes Theorem.

@@

\response{I think we are in agreement that it is common to encounter data sets where a portion of the data is 'good' and a portion of the data is 'bad' (your point (i)).  The 'bad' data may be bad for many reasons, including a breakdown of the measurement process, misrecorded data, and cases that simply aren't relevant to the problem at hand.  The ability to perform a decent analysis for such data sets is important.  And the typical decent analysis focuses on (ii).  We would have little interest in predicting misrecorded test data in a typical situation or in predicting the recorded values when the measurement process has broken down.

@@

\response{'The advantages and disadvantages of the method are detailed throughout the paper using simulated and real data. One conceptual advantage of our method is that inferences and predictions are less sensitive to features of the data not captured by
the conditioning statistics than are methods based on the complete likelihood. Choosing statistics targeting the main features of interest allows for inference that focuses on these features. The analysis can help to better understand other features which may not be captured by the conditioning statistics, such as outliers.'}

@@

\response{Thanks for pointing out the wish by some to have default choices for $f$ and $T$.  We consider regression analysis to be so fundamental to the discipline of statsitics and to the practice of data analysis that we feel it inappropriate to specify defaults in a heavy-handed fashion.  This would be much like specifying a default likelihood if one wishes to build a regression model.  Inthe usual regression setting, many would choose to use a constant variance normal likelihood, as we have done in our examples, but we feel it inappropriate to call this a default likelihood.  As you note, choice of the likelihood is part of the analysis when building a Bayesian model.  To this, we add choice of the conditioning statistic $T$ and illustrate the impact of different choices.  Omission of the formal description of the particular M-estimators that we use is an oversight.

@@

\response{'Finally, it is clear the estimators themselves must be computed for every iteration of the Markov Chain. We have found this burden to be marginal in comparison to computing the needed Jacobian. In the simulations and real data analyses presented below, we will see that the additional computational expense needed to fit the Bayesian model is often worthwhile, leading to better performance compared to traditional, non-Bayesian robust regression estimators.  This is most evident when substantive prior information is available and information in the data is limited.'}

@@

\response{To address the concern you have raised, we have changed our evaluation metric in the simulation to a closed form version of KL divergence.  We use the KL divergence between two normals: $ 
\log(\hat\sigma_{i}^{2}) - \log(\sigma^{2}) + \frac{1}{\hat\sigma_{i}^{2}}(\sigma^{2} + (\theta_{i} - \hat{\theta_{i}})^{2}
$
While we wouldn't be able to compute this in a real application, it does combines estimation error for both the $\theta_{i}$ and $\sigma$ and is a decent metric to compare the methods under the simulation setup. }
John - I'm puzzled by this one.  I'll have to check the paper when I get dropbox up and running again.  (Steve)

@@

\response{Thanks for noticing this detail. It is most natural if it is mutually absolutely continuous with respect to the distribution induced by the model on S.  For the cases we discuss, this is mutually absolutely continuous with respect to the uniform distribution on S.  We now mention the importance of the support.  We have also included a description of what we use for p throughout based on a previous comment. This comment is after Theorem 4.6.}

@@

\response{Thanks for noticing this typo - based on your other comment on KL divergence, this formula was taken out and now is a closed form version. }

@@

\response{We have included some 'default choices' in the paper and in the Supplement.  Information for where to obtain code on Github (an R package as well as data and code for the examples) is now provided in the Introduction.  As noted in our response to Referee 2, we hesitate to push the notion of a default likelihood and default conditioning statistic.  The paper provides a conceptual framework for data analysis and develops the methodology and computation needed to implement the analysis.  We do not view the work as developing an algorithm into which one should just feed data.}

>>>>

\response{This idea is in perfect alignment with our work.  You are right that $T(y_{obs})$ need not be unbiased -- in fact, it need not even be an estimator (think of sums of squares in an ANOVA setting as opposed to mean squares).  It is merely a statistic upon which we condition when using Bayes Theorem.

@@

\response{I think we are in agreement that it is common to encounter data sets where a portion of the data is `good' and a portion of the data is `bad' (your point (i)).  The `bad' data may be bad for many reasons, including a breakdown of the measurement process, misrecorded data, and cases that simply aren't relevant to the problem at hand.  The ability to perform a decent analysis for such data sets is important.  And the typical decent analysis focuses on (ii).  We would have little interest in predicting misrecorded test data in a typical situation or in predicting the recorded values when the measurement process has broken down.

@@

\response{`The advantages and disadvantages of the method are detailed throughout the paper using simulated and real data. One conceptual advantage of our method is that inferences and predictions are less sensitive to features of the data not captured by
the conditioning statistics than are methods based on the complete likelihood. Choosing statistics targeting the main features of interest allows for inference that focuses on these features. The analysis can help to better understand other features which may not be captured by the conditioning statistics, such as outliers.'}

@@

\response{Thanks for pointing out the wish by some to have default choices for $f$ and $T$.  We consider regression analysis to be so fundamental to the discipline of statsitics and to the practice of data analysis that we feel it inappropriate to specify defaults in a heavy-handed fashion.  This would be much like specifying a default likelihood if one wishes to build a regression model.  In the usual regression setting, many would choose to use a constant variance normal likelihood, as we have done in our examples, but we feel it inappropriate to call this a default likelihood.  As you note, choice of the likelihood is part of the analysis when building a Bayesian model.  To this, we add choice of the conditioning statistic $T$ and illustrate the impact of different choices.  Omission of the formal description of the particular M-estimators that we use is an oversight.

@@

\response{`Finally, it is clear the estimators themselves must be computed for every iteration of the Markov Chain. We have found this burden to be marginal relative to computation of the needed Jacobian. In the simulations and real data analyses presented below, we will see that the additional computational expense needed to fit the Bayesian model is often worthwhile, leading to better performance compared to traditional, non-Bayesian robust regression estimators.  This is most evident when substantive prior information is available and information in the data is limited.'}

@@

\response{To address the concern you have raised, we have changed our evaluation metric in the simulation to mean squared error (MSE).  Evaluation via MSE shows a uniform advantage for our restricted likelihood methods relative to classical robust estimators.  We have rewritten the summary of the simulation section.  In doing so, we describe the pattern apparent in the MSE and retain a link to the evaluation via KL-divergence.  We retain this link because the comparisons under KL-divergence do not uniform superiority of our methods as do those based on MSE.}

@@

\response{Thanks for noticing this detail. It is most natural if it is mutually absolutely continuous with respect to the distribution induced by the model on S.  For the cases we discuss, this is mutually absolutely continuous with respect to the uniform distribution on S.  We now mention the importance of the support.  We have also included a description of what we use for p throughout based on a previous comment. This comment is after Theorem 3.6.}

@@

\response{Thanks for noticing this typo - based on the comment on KL divergence, this formula was taken out in favor of MSE. }

@@

\response{We have included some `default choices' in the paper and in the Supplement.  Information for where to obtain code on Github (an R package as well as data and code for the examples) is now provided in the Introduction.  As noted in our response to Referee 2, we hesitate to push the notion of a default likelihood and default conditioning statistic.  The paper provides a conceptual framework for data analysis and develops the methodology and computation needed to implement the analysis.  We do not view the work as developing an algorithm into which one should just feed data.}

### 2020-11-02 revision_2/revision_Jun2020.tex
clean up and add abc analysis script

\response{The performance of the methods can be evaluated in many ways.  For these simulations, we know the true data generating mechanism, and this allows us to make direct comparisons between the fitted model and the truth.  The Bayesian methods provide a full predictive distribution for the response, given group while the classical methods provide only point estimates of parameters.  Our comparisons have focused on two main summaries.  One summary, not presented here, is the average Kullback-Liebler divergence from the good portion of the true distribution of $Y$ given group to the predictive distribution (Bayes) or distribution with point estimates plugged in (classical).  For the Bayesian models, the divergence does not have a closed form and must be evaluated numerically.  The second summary, preferred by a referee, is the mean squared error (MSE), averaged across groups.  Results are presented in Figures \ref{mse_sim} and \ref{mse_mnp}.  Formally, with the superscript $M$ indicating the method and the additional subscript $k$ indexing the data set,
%\begin{equation}
\begin{align}
\label{MSE}
\mbox{MSE}^{(M)}_{ik} & = (\hat\theta^{(M)}_{ik} - \theta_{ik})^2,  \\ 
\mbox{MSE}^{(M)} & = \frac{1}{90K} \sum_{k = 1}^{K} \sum_{i=1}^{90} \mbox{MSE}^{(M)}_{ik}
\end{align}
%\end{equation}

The Bayesian restricted likelihood methods show superior performance under both summaries, but especially for MSE.  Figure \ref{mse_sim} displays the MSE grouped by pairs $a_{s}$ and $c$ with error bars plus/minus one standard error within the group.  The values of $a_{s}$ and $c$, do not affect the classical robust linear models. The average MSEs for the normal theory models ranges from $0.24$ to $0.25$ and are left out of the figure.  The results uniformly favor the Bayesian restricted likelihood methods, as seen by substantially lower values of MSE.  For both classical and restricted likelihood methods, Tukey's $\psi$ function leads to better performance than does Huber's $\psi$ function.  }
%For $c = 0.5$ and $c = 1$ the results favor the restricted likelihood methods as seen by the lower values of loss. The choice of $c = 2$ corresponds to a particularly poor prior distribution.  The prior has substantial mass above $\sigma^{2} = 4$, with prior means for $\sigma^2$ from $8.9$ to $32$ as $a_s$ varies.  Additionally, the tuning parameters chosen for the location and scale estimators result in an upward bias in the estimate of $\sigma^{2}$. This bias depends on $m$ and $p$. For example, for $m = 9$ and $p = .1$, Huber's version converges to roughly $4.8$ as $n$ grows.  The bias is greater for more severe levels of contamination.  The alignment of biases in prior distribution and in likelihood from the summary statistic (when applied to the contaminated data) inflates the estimate of scale.  Not surprisingly, a poor prior distribution whose weakness matches the weakness in the likelihood results in poorer inference.  In this case, poorer than the classical estimators. .  }

@@

\response{It is also interesting to consider the effects of factors $n$, $p$, and $m$.  We present the results for a single prior ($a_s = 5$ and $c = 1$).  For each simulation $k$, the main effect average MSE is found for each factor $n$, $p$, and $m$. Figure \ref{mse_mnp} displays the average MSE over the $K = 30$ simulations along with error bars plus/minus one standard error. For each group $n$, $p$, and $m$, the Bayesian restricted likelihood versions have better average loss than do the classical methods. As expected, the average MSE gets larger as the contamination gets more severe (larger $m$ or larger $p$) and tends to get smaller as the sample size $n$ grows.  The advantage of the Bayesian methods is greater for smaller sample sizes and for less severe contamination.}

@@

\response{This simulation shows the potential of the restricted likelihood methods to dramatically improve estimation.  The simulation also conveys some cautions that are apparent from consideration of KL divergence but not MSE.  Specifically, the choice of summary statistics, along with corresponding tuning parameters is important. For the tuning parameters, we applied the default choice of $95\%$ efficiency at the normal.  Under the simulation model here, this choice results in bias in the scale estimation which affects the performance of the method. These choices must be made when using both the classical and Bayesian methods. The Bayesian approach encourages use of a hierarchical model structure and allows one to incorporate prior information in the analysis.  These features can improve predictive performance substantially.  If poorly handled, they can, of course, harm performance. }

>>>>

\response{The performance of the methods can be evaluated in many ways.  For these simulations, we know the true data generating mechanism, and this allows us to make direct comparisons between the fitted model and the truth.  The Bayesian methods provide a full predictive distribution for the response, given group, while the classical methods provide only point estimates of parameters.  Our comparisons have focused on two main summaries.  One summary, not presented here, is the average Kullback-Liebler divergence from the good portion of the true distribution of $Y$ given group to the predictive distribution (Bayes) or to the distribution with point estimates plugged in (classical).  For the Bayesian models, the divergence does not have a closed form and must be evaluated numerically.  The second summary, preferred by a referee, is the mean squared error (MSE), averaged across groups.  Results are presented in Figures \ref{mse_sim} and \ref{mse_mnp}.  Formally, with the superscript $M$ indicating the method and the additional subscript $k$ indexing the data set,
%\begin{equation}
\begin{align}
\label{MSE}
\mbox{MSE}^{(M)}_{ik} & = (\hat\theta^{(M)}_{ik} - \theta_{ik})^2,  \\ 
\mbox{MSE}^{(M)} & = \frac{1}{90K} \sum_{k = 1}^{K} \sum_{i=1}^{90} \mbox{MSE}^{(M)}_{ik}.  
\end{align}
%\end{equation}

The Bayesian restricted likelihood methods show superior performance under both summaries, but especially for MSE.  Figure \ref{mse_sim} displays the MSE grouped by pairs $a_{s}$ and $c$ with error bars plus/minus one standard error within the group.  The values of $a_{s}$ and $c$ do not affect the classical robust linear models. The average MSEs for the normal theory models ranges from $0.24$ to $0.25$ and are left out of the figure.  The results uniformly favor the Bayesian restricted likelihood methods, as seen by substantially lower values of MSE.  For both classical and restricted likelihood methods, Tukey's $\psi$ function leads to better performance than does Huber's $\psi$ function.  }
%For $c = 0.5$ and $c = 1$ the results favor the restricted likelihood methods as seen by the lower values of loss. The choice of $c = 2$ corresponds to a particularly poor prior distribution.  The prior has substantial mass above $\sigma^{2} = 4$, with prior means for $\sigma^2$ from $8.9$ to $32$ as $a_s$ varies.  Additionally, the tuning parameters chosen for the location and scale estimators result in an upward bias in the estimate of $\sigma^{2}$. This bias depends on $m$ and $p$. For example, for $m = 9$ and $p = .1$, Huber's version converges to roughly $4.8$ as $n$ grows.  The bias is greater for more severe levels of contamination.  The alignment of biases in prior distribution and in likelihood from the summary statistic (when applied to the contaminated data) inflates the estimate of scale.  Not surprisingly, a poor prior distribution whose weakness matches the weakness in the likelihood results in poorer inference.  In this case, poorer than the classical estimators. .  }

@@

\response{It is also interesting to consider the effects of factors $n$, $p$, and $m$.  We present the results for a single prior ($a_s = 5$ and $c = 1$).  For each simulation $k$, the main effect average MSE is found for each factor $n$, $p$, and $m$. Figure \ref{mse_mnp} displays the average MSE over the $K = 30$ simulations along with error bars plus/minus one standard error. For each group $n$, $p$, and $m$, the Bayesian restricted likelihood versions have better average loss than do the classical methods. As expected, the average MSE gets larger as the contamination gets more severe (larger $m$ or larger $p$) and tends to get smaller as the sample size $n$ grows.  The advantage of the Bayesian methods is greater for smaller sample sizes and for more severe contamination.}

@@

\response{This simulation shows the potential of the restricted likelihood methods to dramatically improve estimation.  The simulation also conveys some cautions that are apparent from consideration of KL divergence but not MSE.  Specifically, the choice of summary statistic along with the corresponding tuning parameters is important. For the tuning parameters for the $\psi$ functions, we applied the default choice of $95\%$ efficiency at the normal.  Under the simulation model here, this choice results in bias in the scale estimation which affects the performance of the method. Tuning parameters must be set when using both classical and Bayesian methods. The Bayesian approach encourages use of a hierarchical model structure and allows one to incorporate prior information in the analysis.  These features can improve predictive performance substantially.  If poorly handled, they can, of course, harm performance. }
